Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-16 exp1/present2013.tex
small changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@688 43ef1190-90fd-4dd7-a769-d0121f02b80e
final tweaking
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@689 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}
\documentclass[english,usenames,dvipsnames,aspectratio=169]{beamer}
\usepackage{verbatim}
\usepackage{config}

@@

%\setbeameroption{show only notes}
\usepackage[utf8]{inputenc}

@@

\end{frame}
\note{There are 3 factors, 8 experiments, which is $2^3$}

@@

  \begin{itemize}
  \item Interaction effects may be complex, like one implementation is
    better on CONSTRUCT queries, on small datasets
\end{itemize}
}

@@

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}
\note{We first study a full factorial, in the paper we have three
  fractional, we shall see the final fractional}

@@

\end{frame}
\note{
  \begin{itemize}
  \item ``Machine'' is a broad factor, good idea to group to manage
    complexity, can be broken down later
  \item ``TripleC:Machine'' and ``TripleC'' highly significant,
    implies the factors were wrongly set.
  \item This invalidates the preceeding experiments. We got
    strong indications early on.
  \end{itemize}
}

@@

  \begin{itemize}
  \item Different strategies must be tried, open field.
  \item Formal methods from AI?
  \item Parameterization is very important.
    \begin{itemize}
    \item Data heterogeneity, skewed distributions, etc.
    \item Parameterizing SPARQL queries, see e.g. SPLODGE by Görlitz
      et al.
    \item Parameterizing SPARQL queries using the grammar pragmatically?
    \end{itemize}
  \end{itemize}

\end{frame}
\note{Optimization parameters, hardware characteristics}

@@

\section{Conclusion}

\begin{frame}{Conclusion}
We saw
  \begin{itemize}
  \item ... an experimental setup using DoE.
  \item ... how the analysis pointed out the important effects.
  \item ... how we got a comprehensive view of the experiment.
  \item ... how hypothesis tests could be formulated.
  \item ... how 2-level experiments can determine significant effects,
    even though it is not good enough for modelling.
  \item ... how more economic experiments can be designed, and noted
    their limitations.
  \item ... finally how the experiment could be shown to be flawed.
  \end{itemize}
\end{frame}

>>>>

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}
\documentclass[english,usenames,dvipsnames,aspectratio=169,handout]{beamer}
\usepackage{verbatim}
\usepackage{config}
\usepackage{pgf}
\usepackage{pgfpages}

%
%  Load other packages you may need here
% 
% \pgfpagesuselayout{4 on 1}[a4paper,landscape,border shrink=5mm
\pgfpagesuselayout{2 on 1}[a4paper,border shrink=5mm]

@@

\setbeameroption{show notes}
\usepackage[utf8]{inputenc}

@@

@@

  \begin{itemize}
  \item The main effect of a 2-level factor is the average of the
    observed values on the second level minus the corresponding
    average of the first.
  \item Interaction effects may be complex, like one implementation is
    better on CONSTRUCT queries, on small datasets
\end{itemize}
}

@@

    \begin{itemize}
    \item When experimental economy is important,
    \item DoE theory offers extensive facilities for running a
      fraction of the runs ($2^{n-1}$ etc).
    \item The price is of smaller experiments is explanatory power.
    \end{itemize}
  \end{itemize}
\end{frame}
\note{
  \begin{itemize}
  \item These are called fractional experiments, and come in two
    shapes, full, as we have seen a design matrix of, and fractional. 
  \item With fractional, we trade explanatory power for economy.
  \item We first study a full factorial, in the paper we have three
    fractional, we shall see the final fractional
  \end{itemize}
}

@@

\end{frame}
\note{
  \begin{itemize}
  \item ``Machine'' is a broad factor, good idea to group to manage
    complexity, can be broken down later
  \item ``TripleC:Machine'' and ``TripleC'' highly significant,
    implies the factors were wrongly set.
  \item This invalidates the preceeding experiments. We got
    strong indications early on. This is one of the strategies for
    falsification we outline.
  \item This experiment is also invalidated by the absence of certain
    features, such as language modifiers.
\end{itemize}
}

@@

  \begin{itemize}
  \item Different strategies must be tried, open field.
  \item Parameterization is very important.
    \begin{itemize}
    \item Data heterogeneity, skewed distributions, etc.
    \item Parameterizing SPARQL queries, see e.g. SPLODGE by Görlitz
      et al.
    \item Parameterizing SPARQL queries using the grammar pragmatically?
    \item Formal methods from AI?
    \end{itemize}
  \end{itemize}

@@

\section{Conclusions}

\begin{frame}{Conclusion}
We saw (and the paper details):
  \begin{itemize}
  \item ... an experimental setup using DoE.
  \item ... how the analysis pointed out the important effects.
  \item ... how we got a comprehensive view of the experiment.
  \item ... how hypothesis tests could be formulated.
  \item ... how 2-level experiments can determine significant effects,
    even though it is not good enough for modelling.
  \item ... how more economic experiments can be designed, and noted
    their limitations.
  \item ... finally how the experiment could be shown to be flawed.
  \end{itemize}
\end{frame}
